### 2020-05-28 writeup/transfer.tex
sec 4 wip

Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena of multi-task learning.
We show that negative transfer may result from three factors, including model dissimilarity, data size and covariate shift.
Furthermore, we describe two benefits of multi-task learning, including de-noising via less noisy source labels and improving labeled data efficiency.

%After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
%Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.

>>>>

Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena in multi-task learning.
We explain three contributing causes of negative transfer, including model dissimilarity, large source data size and covariate shift.
On the positive side, we describe two benefits of multi-task learning, including improving labeled data efficiency and de-noising via less noisy source labels.
